
---
output: # rmarkdown::github_document
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 4 - Data Wrangging with `dplyr`"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment4.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- Notice that if there is `eval=FALSE` in the first line of the code chunk, the chunk will not be execute.

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas under Assignment 4. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```

-------

#### 1. Install `tidyverse` package

An R package can be installed by `install.packages` function. Install `tidyverse` if you have not done so. 

```{r}
#install.packages('tidyverse')
#I commented the line above out because it wouldn't let me knit with this line
```

-------

#### 2. Read the data using `read_csv`

Use `read_csv` function to import the US Covid 19 data at [link](https://covidtracking.com/data/download/all-states-history.csv).  Don't forget to import `tidyverse` (library(tidyverse)) so that you can use read_csv. 
```{r}
library(tidyverse)
df <- read_csv("https://covidtracking.com/data/download/all-states-history.csv")
```


-------

#### 3.  Fix the date and ceate some new variables

`lubridate` is a package of the `tidyverse` packages.  We will make uses of `lubridate` in this question.

- Use the below codes to create `month`, `weekday` and `monthday` variables

```{r}
library(lubridate)
df$month = month(df$date)

df$weekday = wday(df$date)

df$monthday <- mday(df$date)
```

-------

#### 4. Create new variables with `case_when`. 

The function `case_when` is a good option to create a new variable from existing variable.  For example, this below codes create a new variable, `daily_death`, from `deathIncrease` variable.  `deathIncrease` is the number of daily new death by Covid19.  The new variable `daily_death` takes three values:  low (if `deathIncrease` less than 3), medium (`deathIncrease` from 3 to 14), and high (`deathIncrease` more than 14).  Please notice that this can also be done in a different way as shown in Assignment 3. 

```{r}
df$daily_death <- case_when(
  df$deathIncrease <3 ~ 'low',
  df$deathIncrease <=14 ~ 'medium',
  TRUE ~ 'high')
```

- Create variable `month2` that takes three values: early_month (day of the month from 1-10), mid_month (day of the month from 11-20), and end_month (day of the month > 20).
```{r}
df$month2 <- case_when(
  df$monthday <=10 ~ 'early_month',
  df$monthday <=20 ~ 'mid-month',
  TRUE ~ 'end_month')
```

- Create variable `weekend` that takes two values:  1 if it's Saturday or Sunday or 0 otherwise. 
```{r}
df$weekend <- case_when(
  df$weekday == 1 ~ 1, df$weekday == 7 ~ 1, TRUE ~ 0)
```

-------

#### 5. Select function

Use the select function to deselect the column `totalTestsViral` from the data.
```{r}
df %>% select(-totalTestsViral)
```

-------

#### 6. Pipe Operator ( %>% )

Pipe operator offers another way to write R codes. Many times, it makes the codes more readable.  Pipe works very well with all the `tidyverse` packages. Refer to [these slides](../slides/4_dplyr.html#15) (slide 15, 16, 17 and 18) to rewrite the below codes using pipe operator

```{r}
x <- c(1:10)

# square root of x
sqrt(x)
x %>% sqrt

sum(sqrt(x))
x %>% sqrt %>% sum

log(sum(sqrt(x)))
x %>% sqrt %>% sum %>% log

# log base 2 of 16
log(16, 2)

```

-------

#### 7. Combo 1: group_by + summarise

This combo is used when you want to apply a function/calculation to different groups of the data. For example, to calculate the average number of cases (`positiveIncrease`) by `dataQualityGrade`, we use:

```{r}
df %>% 
  group_by(weekday) %>% 
  summarise(mean(positiveIncrease))
```

- Calculate the median number of cases (`positiveIncrease`) by `month`
```{r}
df %>% 
  group_by(month) %>%
  summarise(median(positiveIncrease))
```

- Calculate the average number of cases (`positiveIncrease`) by `month2`
```{r}
df %>% 
  group_by(month2) %>%
  summarise(mean(positiveIncrease))
```

- Calculate the median number of cases (`positiveIncrease`) by `weekend`
```{r}
df %>% 
  group_by(weekend) %>%
  summarise(median(positiveIncrease))
```


-------

#### 8. Combo 2: filter + group_by + summarise

An example: to calculate the average number of cases (`positiveIncrease`) in January and February separately, we use:

```{r}
df %>% 
  filter(month==1|month==2) %>% 
  group_by(month) %>% 
  summarise(positive_increase = mean(positiveIncrease))
```

- Calculate the median number of cases (`positiveIncrease`) on the weekend by `month` in October and November 2020. 
```{r}
df %>% 
  filter(month==10|month==11|weekend==1) %>% 
  group_by(month) %>% 
  summarise(positive_increase = median(positiveIncrease))
```

- Calculate the average number of death at different periods of a month (`month2` variable) in Fall 2020
```{r}
df %>% 
  filter(month==9|month==10|month==11) %>% 
  group_by(month2) %>% 
  summarise(fall_deaths = mean(death))
```

- Compare the average number of hospitalizations between weekdays and weekends in Summer 2020
```{r}
df <- df[!(is.na(df$hospitalized)), ]
df %>% 
  filter(month==6|month==7|month==8) %>% 
  group_by(weekend) %>% 
  summarise(hospitalized = mean(hospitalized))
```

- Redo Questions 14 and 15 in [Assignment 3](assignment3.html) using the combos.  Notice:  you also need to use the data used in Assignment 3.  
```{r}
df1 <- read.csv("https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-states.csv")

df1$date = date(df1$date)

df1$weekday = weekdays(df1$date)

# Question 14: Find the median cases by weekdays in Rhode Island in 2021
df1 %>%
  filter(date >= '2021-01-01' & date <= '2021-12-31' & state == 'Rhode Island')%>%
  group_by(weekday) %>%
  summarise(median = median(cases))
```
```{r}
# Question 15: Compare the median cases in Rhode Island in June, July, August and September in 2021

df1$month = month(df1$date)

df1 %>%
  filter(date >= '2021-01-01' & date <= '2021-12-31' & state == 'Rhode Island') %>%
  filter(month == 6|month == 7|month == 8| month == 9)%>%
  group_by(month) %>%
  summarise(median = median(cases))

```

-------

#### 9. Combo 3: filter + group_by + summarise + arrange

Use the arrange function to find a month that has the highest number of deaths on the weekend. 
```{r}
df %>%
  filter(weekday == 1|weekday == 7) %>%
  group_by(month) %>%
  arrange(desc(death))
```

-------

#### 10. Use your own dataset and implement the follows functions or combos. You can use the [Adult Census Income](../data/adult_census.csv) or [Titanic data](../data/titanic.csv). 
```{r}
df2 = read.csv('adult_census.csv')
# in this section I sliced the top 10 results where relevant because otherwise the code would be far too long
```

- select
```{r}
df2 %>%
  select(education) %>%
  slice(1:10)
```

- filter
```{r}
df2 %>%
  filter(sex == 'Male') %>%
  slice(1:10)
```

- mutate
```{r}
df2 %>%
  mutate(education_work.amount = education.num/hours.per.week)%>%
  slice(1:10)
```

- summarise
```{r}
df2 %>%
  summarise(mean(hours.per.week))
```

- arrange
```{r}
df2 %>%
  arrange(desc(education.num)) %>%
  slice(1:10)
```

- count
```{r}
df2 %>%
  count(education = 'HS-grad')
```

- count + arrange
```{r}
df2 %>%
  arrange(desc(age)) %>%
  count(sex = 'Male')
```

- filter + count + arrange
```{r}
df2 %>%
  filter(age < 70) %>%
  arrange(desc(education.num)) %>%
  count(capital_loss = capital.loss) %>%
  slice(1:10)
```

- group_by + summarise
```{r}
df2 %>%
  group_by(race) %>%
  summarise(mean(age))
```

- filter + group_by + summarise
```{r}
df2 %>%
  filter(age < 65) %>%
  group_by(age) %>%
  summarise(median(education.num)) %>%
  slice(1:10)
```

- filter + group_by + summarise + arrange
```{r}
df2 %>%
  filter(age > 30) %>%
  group_by(race) %>%
  summarise(ed_num = mean(education.num)) %>%
  arrange(desc(ed_num))
```
