
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 14: Twitters Mining with rtweet"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment14.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```


[Sample Codes](https://bryantstats.github.io/math421/slides/16_text_mining_rtweet.html)

-------
```{r}
library(rtweet) 
library(tidytext)
library(ggpubr) 
library(tidyverse) 
library(knitr)
library(lubridate)
library(emo)
```

1. Pick a keyword or hashtag. Download the data associated with the keyword/hashtag. Plot at least 5 plots to visualize the data associated with the keyword/hashtag. All plots should have titles and captions. 
```{r,eval=FALSE}
auth_setup_default()

keyword_search = '#Dragonflight'

df <- search_tweets(q = keyword_search, 
                        n = Inf, # number of tweets
                        include_rts = FALSE,
                        `-filter` = "replies",
                        lang = "en") %>% 
  mutate(created_at = ymd_hms(format(created_at, tz = "US/Eastern")))

write_csv(df,'twitterdata.csv')
```

```{r}
df <- read_csv('twitterdata.csv')

ts_plot(df, "hours") +
  labs(x = NULL, y = NULL,
       title = "Frequency of tweets by time",
       subtitle = paste0(format(min(df$created_at), "%d %B %Y"), " to ", format(max(df$created_at),"%d %B %Y")),
       caption = "Data collected from Twitter's REST API via rtweet") +
  theme_minimal()
```
```{r}
df %>% 
  unnest_tokens(mentions, text, "tweets", to_lower = FALSE) %>%
  filter(str_detect(mentions, "^@")) %>%  
  count(mentions, sort = TRUE) %>%
  head(10) %>% 
  ggplot(aes(x = n, y = reorder(mentions, n)))+
  geom_col()+
  labs(title = 'Most @ mentions',x = '# of mentions', y = '')
```
```{r}
df %>% 
  filter(created_at>='2022-11-14') %>% 
  unnest_tokens(output = hashtag, input = text, token = "tweets") %>%
  filter(!hashtag %in% c("#dragonflight"), str_detect(hashtag, "^#")) %>% 
  count(hashtag, sort = TRUE) %>%
  head(5) %>% 
  ggplot(aes(x = n, y = reorder(hashtag, n)))+
  geom_col()+
  labs(x = 'Frequency', y = '', title = 'other # mentions')
```
```{r}
df %>%
  mutate(emoji = ji_extract_all(text)) %>%
  unnest(cols = c(emoji)) %>%
  count(emoji, sort = TRUE) %>%
  head(5) %>% 
  ggplot(aes(y=reorder(emoji,n), x=n)) +
  geom_col()+
  theme(axis.text.y = element_text(size = 40))+
  labs(title = 'Top Emoji in the tweets', y = '')
```
```{r}
df %>%
    unnest_tokens(input = text, output = word) %>% 
    anti_join(get_stopwords()) %>% 
    count(word, sort = TRUE) %>%
    inner_join(get_sentiments("nrc")) %>%
    filter(!is.na(sentiment)) %>%
    count(sentiment, sort = TRUE) %>% 
    mutate(n = n/sum(n)) %>% 
    ggplot(aes(y= reorder(sentiment, n), x = n))+geom_col()+
    labs(y='Relative Frequency', x ='', title = "sentiment frequencies")
```


2. Choose a location then pick a trending keyword/hashtag in the location. Download the data associated with the keyword/hashtag. Plot at least 5 plots to visualize the data associated with the keyword/hashtag. All plots should have titles and captions. 
```{r eval=FALSE}
get_trends('Providence')
#Anthony Brown was number 5 when doing this
```
```{r,eval=FALSE}
keyword_search = 'Anthony Brown'

df <- search_tweets(q = keyword_search, 
                        n = Inf, # number of tweets
                        include_rts = FALSE,
                        `-filter` = "replies",
                        lang = "en") %>% 
  mutate(created_at = ymd_hms(format(created_at, tz = "US/Eastern")))

write_csv(df, 'twitterdata1.csv')
```

```{r}
df <- read.csv('twitterdata1.csv')

ts_plot(df, "hours") +
  labs(x = NULL, y = NULL,
       title = "Frequency of tweets by time",
       caption = "Data collected from Twitter's REST API via rtweet") +
  theme_minimal()
```
```{r}
df %>% 
  unnest_tokens(mentions, text, "tweets", to_lower = FALSE) %>%
  filter(str_detect(mentions, "^@")) %>%  
  count(mentions, sort = TRUE) %>%
  head(10) %>% 
  ggplot(aes(x = n, y = reorder(mentions, n)))+
  geom_col()+
  labs(title = 'Top 10 mentions in the tweets', y = '')
```
```{r}
df %>% 
  unnest_tokens(output = hashtag, input = text, token = "tweets") %>%
  filter(str_detect(hashtag, "^#")) %>% 
  count(hashtag, sort = TRUE) %>%
  head(5) %>% 
  ggplot(aes(x = n, y = reorder(hashtag, n)))+
  geom_col()+
  labs(x = 'Frequency', title = 'top #s referenced')
```
```{r}
df %>%
  mutate(emoji = ji_extract_all(text)) %>%
  unnest(cols = c(emoji)) %>%
  count(emoji, sort = TRUE) %>%
  head(5) %>% 
  ggplot(aes(y=reorder(emoji,n), x=n)) +
  geom_col()+
  theme(axis.text.y = element_text(size = 40))+
  labs(title = 'Top Emoji in the tweets', y = '')
```
```{r}
df %>%
    unnest_tokens(input = text, output = word) %>% 
    anti_join(get_stopwords()) %>% 
    count(word, sort = TRUE) %>%
    inner_join(get_sentiments("nrc")) %>%
    filter(!is.na(sentiment)) %>%
    count(sentiment, sort = TRUE) %>% 
    mutate(n = n/sum(n)) %>% 
    ggplot(aes(y= reorder(sentiment, n), x = n))+geom_col()+
    labs(y='Relative Frequency', x ='', title = "sentiment frequencies")
```

