
---
output: # rmarkdown::github_document
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 3.  Working with Data Frame. Base R Style"
---

***Note*:** *This assignment practices working with Data Frame using Base R.*

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment3.Rmd)) in Rstudio. 

- Right under each question, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas under Assignment 3. 

-------

Problems
-------
 \

1. Create the following data frame

| Rank 	| Age 	| Name  	|
|:------	|:-----	|:-------	|
| 0    	| 28  	| Tom   	|
| 1    	| 34  	| Jack  	|
| 2    	| 29  	| Steve 	|
| 3    	| 42  	| Ricky 	|
```{r}
Rank <- c(0,1,2,3)
Age <- c(28,34,29,42)
Name <- c("Tom","Jack","Steve","Ricky")
cbind(Rank,Age,Name)
```

2. Use `read.csv` to import the Covid19 Vaccination data from WHO: [link](https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-states.csv).
```{r}
df <- read.csv("https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-states.csv")
```

3. Show the names of the variables in the data
```{r}
names(df)
```

4. How many columns and rows the data have? 
```{r}
ncol(df)
```
```{r}
nrow(df)
```

5. How many missing values are there?  Show the missing values by columns.  What variable has the most number of missing values?
```{r}
sum(is.na(df))
# there is no missing values
```

6. What is the class of the `date` column. Change the `date` columns to `date` type using the `as.Date` function. Show the new class of the `date` column. 
```{r}
df$date <- as.Date(df$date)
class(df$date)
```

7. Capitalize the names of all the variables
```{r}
names(df) <- toupper(names(df))
```

8. Find the average number of cases per day. Find the maximum cases a day.  
```{r}
df1 <- mean(df$CASES)
df1
```
```{r}
df1f <- max(df$CASES)
df1f
```


9. How many states are there in the data?  
```{r}
length(unique(df$STATE))
#56 unique fields in 'state' group
#6 territories
#50 states
```

10. Create a new variable `weekdays` to store the weekday for each rows. 
```{r}
df3 <- df
df3$weekday <- strftime(df3$DATE, "%A")
names(df3)
```

11. Create the categorical variable `death2` variable taking the values as follows

- `has_death` if there is a death that day
-  `no_death` if there is no death that day
```{r}
df3$death2 <- ifelse(df3$DEATHS==0,'no_death','has_death')
table(df3$death2)
```

Find the frequency and relative frequency of `no_death` and `has_death`. 
```{r}
table(df3$death2)
```
```{r}
prop.table(table(df3$death2))
```

12. Find the first quartile (Q1), second quartile (Q2) and and third quartile (Q3) of the variable `death`. (Hint:  Use the `summary` function)
```{r}
quantile(df3$DEATHS)
```

13. Create the categorical variable `death3` variable taking the values as follows

- `low_death` if the number of deaths smaller than the 25 percentile (Q1)

- `mid_death` if the number of deaths from Q1 to Q3

- `high_death` if the number of deaths greater than Q3
```{r}
df3$death3 <- ifelse(df3$DEATHS<quantile(df3$DEATHS)[2],'low_death',ifelse(df3$DEATHS<quantile(df3$DEATHS)[4],"mid_death",'high_death'))
table(df3$death3)
```


14. Find the average cases in Rhode Island in 2021
```{r}
df4 <- df3[(df3$DATE>='2021-01-01')&(df3$DATE<='2021-12-31'),]
df4 <- df4[df4$STATE=='Rhode Island',]
mean(df4$CASES)
```

15. Find the median cases by weekdays in Rhode Island in 2021 
```{r}
by(df4$CASES,df4$weekday,median)
```

16. Compare the median cases in Rhode Island in June, July, August and September in 2021. 
```{r}
df4$MONTHS <- strftime(df4$DATE, "%B")
df5 <- df4[df4$MONTHS %in% c('June','July','August','September'),]
by(df5$CASES,df5$MONTHS,median)
```

17.  Find your own dataset, import it and implement the following functions on the data

- head
- str
- names
- mean, min, max
- table
- is.na
- colSums
- class
- cor
- by
- ifelse
- case_when
```{r}
gao <- read.csv('titanic.csv')
head(gao)
```
```{r}
str(gao)
```
```{r}
names(gao)
```
```{r}
median(gao$Fare)
```
```{r}
mean(gao$Fare)
```
```{r}
max(gao$Fare)
```
```{r}
table(gao$Survived)
```
```{r}
sum(is.na(gao$Fare))
#0 people who did not pay
```
```{r}
ncol(gao)
```
```{r}
class(gao$Fare)
```
```{r}
cor(gao$Pclass,y=gao$Survived,use = "everything",method = 'pearson')
```
```{r}
by(gao$Fare,gao$Survived,mean)
```
```{r}
quantile(gao$Fare)
```
```{r}
gao$fare2 <- ifelse(gao$Fare<quantile(gao$Fare)[2],'low_fare', ifelse(gao$Fare<quantile(gao$Fare)[3],'mid_low_fare', ifelse(gao$Fare<quantile(gao$Fare)[4],'mid_high_fare', 'high_fare')))
#this answers bullet 1 of question 18 by creating a categorical variable
head(gao)
```

```{r}
library(dplyr)
gao$buyer <-case_when(gao$Age>=18 ~ "Bought Ticket", TRUE ~ "Minor")
head(gao)
```


18.  In the dataset in #17, practice the follows.  You can reuse the code of 17. 

- Create a categorical variable from a continuous variable
- From one categorical variable, create a new categorical variable with fewer categories

If you do not have a data, you can use [the titanic dataset](https://www.kaggle.com/competitions/titanic/overview), which can be downloaded at [this link](../data/titanic.csv)
```{r}
library(tidyverse)
gao$farelowhigh <- ifelse(str_detect(gao$fare2,'low'),'low','high')
head(gao)
```

