
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 15: Writing a function - Conditional Statement"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment15.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```

-------

#### NOTICE: Question 7, 8 and 9 are optional. 

-------

1. Write a function to calculate the age of a person.  Give an example to test your function. 

- Input: a number, x, (year born)

- Output: Print out "You are r age". Where r is the age of the person, i.e. 2020 - x. 

Hint: [Similar Function](https://bryantstats.github.io/math421/gganimate/17_writing_functions.html#42)

```{r}
age <- function(x)
{
  y = 2022 - x
  print(paste0('You are ', y, ' age'))
}
age(2001)
```

-------

2. Write the following function. Give an example to test your function. 

- Input: a number

- Output: print out: "You input an even number!" if the number is event, or "You input an odd number!" otherwise. 

Hint: [Similar Function](https://bryantstats.github.io/math421/gganimate/17_writing_functions.html#46)
```{r}
num <- function(x)
{
  if(x %% 2 == 0)
  {
    print('You input an even number!') 
  }
  else
  {
    print('You input an odd number!')
  }
}
num(4)
```

-------

3. Write the following function.  Give an example to test your function. 

- Input: a numeric vector 

- Output:  

  - if the input vector has missing values: return the input vector with missing values replaced by mean
  
  - if the input vector has no missing value: return the same input vector
  
Hint: [Similar Function](https://bryantstats.github.io/math421/gganimate/17_writing_functions.html#50)
```{r}
removena <- function(x)
{
  if(anyNA(x) == TRUE)
  {
    x=x[!is.na(x)]
    return(x)
  }
  else
  {
    return(x)
  }
}

a <- c(1,2,NA,4,5,NA,7)

removena(a)
```

-------

4. Write the following function.  Give an example to test your function. 

- Input: a vector x 

- Output:  The vector x where the missing values replaced by the mean (if x is numeric) or the mode (if x is non-numeric).  If x does not have missing value, return the same vector x.  

Hint: Use If-statement to combine the function in Question 3 and [this function](https://bryantstats.github.io/math421/gganimate/17_writing_functions.html#49)
```{r}
meanmode <- function(x)
{
  if(is.numeric(x))
  {
    mean_x <- mean(x, na.rm=TRUE)
    library(tidyr)
    x <- replace_na(x, mean_x)
    return(x)
  }
  else
  {
    mode_x <- names(sort(-table(x)))[1]
    x <- replace_na(x, mode_x)
    return(x)
  }
}

meanmode(a)
```

```{r}
b <- c("a","a","a",NA,"b",NA)

meanmode(b)
```

-------

5. Write the following function. Give examples to test your function. 

- Input: A data frame of two variables x and y

- Output: 

  - A boxplot of x by y if x is numeric and y is non-numeric
 
  - A boxplot of y by x if y is numeric and x is non-numeric
 
  - print out 'This function cannot visualize your data' otherwise

Hint: 

- [Similar Function](https://bryantstats.github.io/math421/gganimate/17_writing_functions.html#53)
 
- You can refer to this slide to plot a boxplot: https://bryantstats.github.io/math421/slides/6_viz.html#36

```{r}
library(tidyverse)
bplot <- function(z)
{
  if(is.numeric(z[[1]])&&!is.numeric(z[[2]]))
  {
    z %>% ggplot(aes(x = z[[1]], y = z[[2]]))+
      geom_boxplot()+labs(x='',y='')
  }
  else if(is.numeric(z[[2]])&&!is.numeric(z[[1]]))
  {
    z %>% ggplot(aes(x = z[[2]], y = z[[1]]))+
      geom_boxplot()+labs(x='',y='')
  }
  else
  {
    print('This function cannot visualize your data')
  }
}

x <- c(1,2,3,4,5,6)
y <- c('odd','even','odd','even','odd','even')
z <- data.frame(x,y)

bplot(z)
```
```{r}
z <- data.frame(y,x)

bplot(z)
```
 
-------
 
6. Combine the function in Question 5 and the function in this example ([Link](https://bryantstats.github.io/math421/gganimate/17_writing_functions.html#53)) to have a function that can plot all possible cases (2 categorical, 2 numeric, 1 numeric and 1 categorical). 
```{r}
bplot2 <- function(z)
{
  if(is.numeric(z[[1]])&&!is.numeric(z[[2]]))
  {
    z %>% ggplot(aes(x = z[[1]], y = z[[2]]))+
      geom_boxplot()+labs(x='',y='')
  }
  else if(is.numeric(z[[2]])&&!is.numeric(z[[1]]))
  {
    z %>% ggplot(aes(x = z[[2]], y = z[[1]]))+
      geom_boxplot()+labs(x='',y='')
  }
  else if(is.numeric(z[[1]])&&is.numeric(z[[2]]))
  {
    z %>% ggplot(aes(x = z[[1]], y = z[[2]]))+
      geom_point()+labs(x='',y='')
  }
  else if(!is.numeric(z[[1]])&&!is.numeric(z[[2]]))
  {
     z %>% ggplot(aes(x = z[[1]], fill = z[[2]]))+
      geom_bar(position = 'dodge')+
      labs(x = names(z)[1], fill = names(z)[2])
  }
  else
  {
    print('This function cannot visualize your data')
  }
}

z1 <- data.frame(c(1,2,3,4,5),c(1,4,9,16,25))
bplot2(z1)
```
```{r}
odds <- c('odd','even','odd','even','odd','even','odd','even','odd','even')
primes <- c('p','p','p','np','p','np','p','np','np','np')
z2 <- data.frame(odds, primes)
bplot2(z2)
```

-------

#### NOTICE: Question 7, 8 and 9 are optional. 

-------

7. Write the following function. Give examples to test your function. 

- Input: 

  - input_data: a clean data frame with a variable name `target`. The `target` variable is also binary. 
  
  - train_percent: a number presenting a proportion of training data. The default train_percent is .8

- Output: the accuracy of the decision model `rpart` where the training data is train_percent. 

-------

8. Write the following function. Give examples to test your function. 

- Input: 

  - input_data: a clean data frame with a variable name `target`. The `target` variable is also binary. 
  
  - train_percent: a number presenting a proportion of training data. The default train_percent is .8

- Output: the plot of variable important by random forest trained by caret. 


---
9. Write the following function. Give examples to test your function. 

- Input: 

  - a data frame that has a text column 
  
  - the name of the text column in the data

- Output: the word cloud plot of the text column

Sample codes

- [Word Cloud codes](https://bryantstats.github.io/math421/assignments/text_mining_sample_codes2.html#Total_Word_Cloud)

- [A similar function](https://bryantstats.github.io/math421/gganimate/17_writing_functions.html#10)


